Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-10 ms.tex
editing intro to low-frequency prediction comparison section

\section{Low-frequency Emission Predictions}
FDS99 originally performed their two-component versus single-MBB dust SED 
analysis for the sake of accurately forecasting low-frequency CMB foregrounds.
The need for accurate CMB foreground predictions, especially in the 100-150 GHz
frequency range, has been highlighted of late by the \cite{bicep2} $B$-mode 
polarization results. In this section we show that our two-component foreground
predictions are more accurate than those based on the single-MBB model of 
\cite{planckdust} over the 100-217 GHz frequency range.

@@

>>>>

\section{Low-frequency Emission Predictions}
FDS99 originally performed their \PLANCK+DIRBE dust SED analysis for the sake 
of accurately forecasting low-frequency CMB foregrounds. Recently, Galactic CMB
foregrounds, especially in the 100-150 GHz frequency range, have become a focal
point of cosmology owing to the \cite{bicep2} $B$-mode polarization results. 
Here we show that our two-component foreground predictions are more accurate 
than those based on the \cite{planckdust} single-MBB model over the 100-217 GHz
frequency range.

@@

%end section saying that the predictions accessible through our data 
% release should be investigated/tested/swapped in by people doing
% B-mode stuff
